### 2018-06-20 Thesis/Parts/Background/Background.tex
shallow total iteration

The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data. \citet{armburst2015} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark. This allows for much tighter intergration between relational and procedural processing. The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines.

>>>>

The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data. \citet{armbrust2015spark} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark. This allows for much tighter intergration between relational and procedural processing. The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines.

### 2018-06-20 Thesis/Parts/Conclusion/Conclusion.tex
shallow total iteration

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level. This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset. This improved embedding results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

### 2018-06-20 Thesis/Parts/Data/Data.tex
shallow total iteration

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & Total word count & Unique word count & Total token count & Unique token count \\
\hline
Title & $18.822.399$ & $939.665$ & $14.742.192$ & $230.805$ \\
\hline
Abstract & $264.653.020$ & $5.853.077$ & $171.474.473$ & $738.961$ \\
\hline
Total & $283.475.419$ & $6.209.769$ & $186.962.354$ & $763.475$ \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}. This distribution is visualized in XXXXXX, which displays the occurrences of the first 500 tokens of the corpus.
\includegraphics[width=6.5in]{Plots/word_occurrences}\\

@@

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
The graph XXX shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see XXXXX} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used CITATIONS NEEDED. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. XXXX shows the results of this validation.\\
\begin{minipage}{6.5in}
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\end{minipage}\\
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant XXX EXPLAIN? XXX. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals. Details about the corpus can be found in table~\ref{table:corpusSize}.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
 & Total count & Unique count & Average length \\
\hline\hline
Title words & $18.822.399$ & $939.665$ & 13,53  \\
\hline
Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
\hline\hline
Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
\hline
Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
\hline\hline
Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
\hline
Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}. This distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/word_occurrences}
\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
\end{figure}

@@

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
\begin{figure}
\includegraphics[width=6in]{Plots/tfidf_selection_plot}
\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
\end{figure}

Figure~\ref{figure:tfidfPerformance} shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\
\begin{table}[hbt]
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
\end{table}
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

### 2018-06-20 Thesis/Parts/Discussion/Discussion.tex
shallow total iteration

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Discussion}
\subheader{Sets}
\subheader{Best performers}
The data shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank (7.14\%) on abstract and 3 median ranks (8.57\%) on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings ourperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains less unique tokens (see XXXXX), this means that the titles contain less unique information, making them more generic. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts cannot differentiate between the highly similar titles. The TF-IDF method works better on the abstract, which contain more unique words, which help in differentiating the different texts. Furthermore, increasing the vocabulary size increases the performance of the TF-IDF, since the vocabulary size is cut-off at word occurrences, which reduces the amount of unique words. 
\subsubheader{Embedding}
\subsubsubheader{Limited tfidf embeddings}
The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. However, graphs XXX and XXX show that their rank distribution is different from the other embeddings. Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Graph XXX), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end. Resulting in low median and average scores, but in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However they can be processed more efficiently during calculations}. This results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case. This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles. The abstracts on the other hand contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (SEE GRAPH XXX). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is worse than the embedding, which also uses less memory.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
\subheader{Sets}
\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains less tokens (see table~\ref{table:corpusSize}), this means that the titles contain less information. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
\subsubheader{Embedding}
\subsubsubheader{Limited tfidf embeddings}
The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results, higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end. Resulting in low median and average scores, but in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However they can be processed more efficiently during calculations}. This results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case. This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles. The abstracts on the other hand contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. 
If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We would also expect on the abstract an increase in performance, since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory. 
\end{document}

### 2018-06-20 Thesis/Parts/Future_work/Future_work.tex
shallow total iteration

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
- How do unique token count, token count and vocabulary size relate for TF-IDF?
- Can high quality word similarity sets be created from embedding for future benchmarking?
- Can embeddings give a visual representation of the evolution of scientific research over time?
- Does TF-IDF improve when top-occurring words are cut-off?
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
- Does the performance of embeddings and TF-IDF improve when embeddings and feature vectors are generated over the combination of title and abstract as one text?\\
	- this helps when dealing with articles that do not have a title or an abstract.\\
- How do unique token count, token count and vocabulary size relate for TF-IDF?\\
- Can high quality word similarity sets be created from embedding for future benchmarking?\\
- Can embeddings give a visual representation of the evolution of scientific research over time?\\
- Does TF-IDF improve when top-occurring words are cut-off?\\
\end{document}

### 2018-06-20 Thesis/Parts/Motivation/Motivation.tex
shallow total iteration

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Motivation}
\subheader{In-domain embeddings and validation}
Earlier research, concerning domain specific articles, by \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering. This effect is even stronger than the number of training examples and the model architecture. \citet{lai2016generate} found that the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
Truong et al. encountered a problem in the validation of these in-domain embeddings. The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality, since they capture the document relatedness needed to create correct clusterings. However unpublished results by Truong et al. state that the embeddings show high error rates on the validation scores. This seems to indicate that the word-vectors are of good quality, but that the available validation metrics cannot confirm this. \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings. However, these set are created to validate the generic embeddings, they fail to asses the quality of the domain specific embeddings.

\subheader{Research}
To asses the problem of the limited availability of pre-labelled validation sets for domain specific articles, we compare the embeddings to  TF-IDF on a categorization task. This A) gives an indication of the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach. To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
\begin{jumpin}
	\textbf{RQ.1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
	\textbf{RQ.2} Which metric can be used to measure the accuracy of word embeddings for scientific articles?
\end{jumpin}
\subsubheader{Embedding and TF-IDF}
Research question one focusses on the classification results of both embedding-based techniques and TF-IDF.  To measure classification task we use the rank of the class to which the item belongs. Transforming the classification task from a binary metric to a ranking metric. For this task, we will use different versions of embeddings, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques. For this part of the research, we will use the following hypothesis:
\begin{center}
\textit{Embedding based techniques give lower rankings than the TF-IDF based techniques}
\end{center}
By validating our invalidating  this hypothesis we get an indication of the performance of the embeddings compare to older techniques, and get insight into possible performance and resource trade-off's and if the computational power and AI expertise needed for the creation of embeddings is worth the investment .

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Motivation}
\subheader{In-domain embeddings and validation}
In earlier research concerning domain specific articles,  \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering. This effect is even stronger than the number of training examples and the model architecture. \citet{lai2016generate} found that the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
Truong et al. encountered a problem in the validation of these in-domain embeddings. The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality, since they capture the document relatedness needed to create correct clusterings. However unpublished results by Truong et al. state that the embeddings show high error rates on the validation scores. This seems to indicate that the word-vectors are of good quality, but that the available validation metrics fail to confirm this. \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings. However, these set are created to validate the generic embeddings, they fail to asses the quality of the domain specific embeddings.

\subheader{Research}
To asses the problem of the limited availability of pre-labelled validation sets for domain specific articles, we compare the embeddings to  TF-IDF on a categorization task. This A) gives an indication of the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach. To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
\begin{jumpin}
	\textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
	\begin{adjustwidth}{0.3in}{}
		\textbf{RQ. 1.1} Does TF-IDF weighting increase the performance of word embedding on academic texts for article classification?\\
		\textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic articles for article classification?
	\end{adjustwidth}
	\vspace{0.1in}\textbf{RQ. 2} Can word embeddings, combined with pca\footnote{principal component analysis}-based TSNE, create a two-dimensional plot that preserves the journal relatedness?
\end{jumpin}
\subsubheader{Embedding and TF-IDF}
RQ. 1 focusses on the classification results of both embedding-based techniques and TF-IDF.  To measure classification task we use the rank of the class to which the item belongs. Transforming the classification task from a binary metric to a ranking metric. For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques. To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings. For this part of the research, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 1} Embedding based techniques give lower rankings than the TF-IDF based techniques.}
\begin{jumpin}
\textit{\textbf{H. 1.1} TF-IDF weighted document embeddings outperform standard embeddings on the classification of academic articles.}\\
\textit{\textbf{H. 1.2} Cosine similarity based ranking results in the best performance for the classification of academic articles.}\\
\textit{\textbf{H. 1.3} Word embeddings use less memory while giving better ranking results than TF-IDF on the classification of academic articles.}
\end{jumpin}
\end{jumpin}
By validating our invalidating  these hypotheses we get an indication of the performance of the embeddings compare to older techniques,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics. 
RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 2} Word embeddings, combined with pca-based TSNE can preserve the journal relatedness on a two dimensional plot.}
\end{jumpin}
The validation of this hypothesis will be visual, this serves as a supporting insight in the relatedness of journals.
